Artículo 1. Uso del tiempo.

### 2022-05-26 Articulo1_LIDE/Draft_Articulo1_LIDE_UT.Rmd
Archivos del Artículo 1 organizados.

```{r include=FALSE}
###############################################################
####               Descarga de los datos                   ####
###############################################################

>>>>

```{r include=FALSE}
###############################################################
####         Importación de las bases de datos             ####
###############################################################
